\toftagthis{anglicke}
\song{Hallelujah}{Leonard Cohen / Jeff Buckley}{30pt}{0.89}{
\verse{1}{}I've \G{}heard there was a \Em{}secret chord,\\
that \G{}David played, and it \Em{}pleased the Lord,\\
but \C{}you don't really \D{}care for music, \G{}do you? \D{}\\
It \G[/H]{}goes like this, the \C{}fourth, the \D{}fifth,\\
the \Em{}minor fall, the \C{}major lift,\\
the \D{}baffled king \H[7]{}composing Halle\Em{}lujah!

\chorus{}Halle\C{}lujah, Halle\Em{}lujah, Halle\C{}lujah, Halle\G{}lu-uu\D{}uu-u\G{}jah! 

\verse{2}{}Your faith was strong, but you needed proof,\\
you saw her bathing on the roof,\\
her beauty and the moonlight overthrew you.\\
She tied you to a kitchen chair,\\
she broke your throne, and she cut your hair,\\
and from your lips she drew the Hallelujah!\\
\textbf{R:}

\optVerse{-35pt}{27pt}{20pt}{
\verse{3}You say I took the name in vain,\\
I don't even know the name,\\
but if I did, well really, what's it to you?\\
There's a blaze of light in every word,\\
it doesn't matter which you heard,\\
the holy or the broken Hallelujah!\\
\textbf{R:}
}
~\\
\verse{4}{}Baby, I've been here before,\\
I know this room, I've walked this floor,\\
I used to live alone before I knew you.\\
I've seen your flag on the marble arch,\\
but love is not a victory march,\\
it's a cold and it's a broken Hallelujah!\\
\textbf{R:}

\verse{5}{}There was a time you let me know,\\
what's really going on below,\\
but now you never show it to me, do you?\\
But I remember, when I moved in you,\\
and the holy dove was moving too,\\
and every breath we drew was Hallelujah!\\
\textbf{R:}

\verse{6}{}Maybe there's a God above,\\
but all I've ever learned from love\\
was how to shoot at someone who outdrew you.\\
But it's not a cry that you hear at night,\\
it's not somebody who's seen the light,\\
it's a cold and it's a broken Hallelujah!\\
\textbf{R:}

\optVerse{-35pt}{27pt}{20pt}{
\verse{7}{}I did my best, it wasn't much,\\
I couldn't feel, so I tried to touch,\\
I've told the truth, I didn't come to fool you.\\
And even though it all went wrong,\\
I'll stand before the Lord of Song\\
with nothing on my tongue but Hallelujah!\\
\textbf{R: $(2\times)$}
}
}


\toftagthis{anglicke}
\song{Help!}{The Beatles}{20pt}{0.89}{
\crdheight=2.3ex
\verse{*}{}\Hm{}Help! I need somebody, \G{}help! Not just anybody,\\
\E{}help! You know I need someone, \A[7]{}help!

\verse{1}{}\A{}When I was younger, so much \Csm{}younger than today,\\
\Fsm{}I never needed anybody's \D{}help in \G{}any \A{}way.\\
But now these days are gone I'm \Csm{}not so self assured,\\
\textls[-25]{\Fsm{}now I find I've changed my mind I've \D{}opened \G{}up the \A{}door.}

\chorus{}\Hm{}Help me if you can I'm feeling down\\
and I \G{}do appreciate you being 'round,\\
\E{}help me get my feet back on the ground,\\
won't you \A{}please, please help me?

\verse{2}{}And now my life has changed in oh so many ways,\\
my independence seems to vanish in the haze.\\
But every now and then I feel so insecure,\\
I know that I just need you like I've never done before.\\
\textbf{R:}

\verse{3}When I was younger\ldots\\
\textbf{R:} \ldots{} please, please help \Fsm{}me, help me, help \A[6]{}me, ooh\ldots{}\\
}


\toftagthis{anglicke}
\song{Hit the Road, Jack}{Ray Charles}{20pt}{1}{
\chorus{}Hit the \Am{}road, \Am[/G]{}Jack, and \F{}don't you come \E{}back\\
no more, no more, no more, no more.\\
Hit the road, Jack, and don't you come back no more.\\
\emph{(What you say?)}\\
Hit the road, Jack, and don't you come back\\
no more, no more, no more, no more.\\
Hit the road, Jack, and don't you come back no more.

\verse{1}Woah Woman, oh woman, don't treat me so mean,\\
You're the meanest old woman that I've ever seen.\\
I guess if you say so\\
I'd have to pack my things and go.\\
\textbf{R:}

\verse{2}Now baby, listen baby, don't ya treat me this-a way\\
Cause I'll be back on my feet some day.\\
Don't care if you do 'cause it's understood\\
you ain't got no money you just ain't no good.\\
Well, I guess if you say so\\
I'd have to pack my things and go.\\
\textbf{R:}\\
\revrpt{} \ldots{}don't you come back no more. \rpt{}\\

}



\toftagthis{nohavica}
\song{Hlídač krav}{Jaromír Nohavica}{40pt}{0.95}{
\verse{1}{}\D{}Když jsem byl malý, říkali mi naši:\\
\uv{Dobře se uč a jez chytrou kaši,\\
\G{}až jednou vyrosteš, \A{}budeš doktorem \D{}práv.}\\
Takový doktor sedí pěkně v suchu,\\
bere velký peníze a škrábe se v uchu,\\
já jim ale na to řek': \uv{Chci být hlídačem krav.}

\chorus{}Já chci mít čapku s bambulí nahoře,\\
jíst kaštany a mýt se v lavoře,\\
od rána po celý den zpívat si jen,\\
zpívat si: pam pam pam\ldots{} 

\verse{2}{}K vánocům mi kupovali hromady knih,\\
co jsem ale vědět chtěl, to nevyčet' jsem z nich,\\
nikde jsem se nedozvěděl, jak se hlídají krávy.\\
Ptal jsem se starších a ptal jsem se všech,\\
každý na mě hleděl jako na pytel blech,\\
každý se mě opatrně tázal na moje zdraví.\\
\textbf{R:}

\verse{3}{}Dnes už jsem starší a vím, co vím,\\
mnohé věci nemůžu a mnohé smím,\\
a když je mi velmi smutno, lehnu si do mokré trávy.\\
S nohama křížem a rukama za hlavou\\
koukám nahoru na oblohu modravou,\\
kde se mezi mraky honí moje strakaté krávy.\\
\textbf{R:}\\
}

\toftagthis{zalman}
\song{Ho ho Watanay}{Pavel Lohonka Žalman / indiánská}{50pt}{1}{
\vskip 8pt
\verse{1}\D{}Spinkej, můj maličký, \C{}máš v očích \D{}hvězdičky,\\
dám ti je \C{}do vlasů, tak \G{}usínej tak \D{}usínej.

\chorus{}\D{}Ho ho Watanay, \C{}ho ho \D{}Watanay,\\
ho ho \C{}Watanay, Ki\G{}okena, Ki\D{}okena.

\verse{2}Sladkou vůni nese ti noční motýl z perleti,\\
vánek ho kolíbá, už usíná, už usíná.\\
\textbf{R:}

\verse{3}V lukách to zavoní, rád jezdíš na koni,\\
má barvu havraní, jak uhání, jak uhání.\\
\textbf{R:}

\verse{4}V dlani motýl usíná, hvězdička už zhasíná,\\
vánek co ji k tobě nes', až do léta ti odlétá.\\
\textbf{R:}\\
}


\toftagthis{anglicke}
\song{Hollywood Hills}{Sunrise Avenue}{20pt}{1}{
\capo{4}
\vskip 2ex
\verse{1}Now this \G{}is not the time or the place for brokenh\D[sus4/F$\sharp$]{}earted,\\
cause this is the end of the \Em[7]{}rainbow,\\
where no one can be\C[add9]{} \hskip 1em too \hskip 1em \Em[7]{}sad. \hskip 1em \D[sus4/F$\sharp$]{}\\
No, I don't wanna leave but I must keep moving ahead,\\
cause my life belongs to the other side,\\
behind the great ocean's waves.

\chorus{}\G{} Bye, bye, Hollywood Hill\G[/H]{}s, I'm gonna\\
\D{} miss you, wherever I g\D[/F$\sharp$]{}o, I'm gonna\\
\Em[7]{} come back to \Em[7/H]{}walk these streets again,\\
\C[add9]{} bye, bye, Hollywood Hi\D{}lls for\G{}ever.

\verse{2}Thank you for the morning walks on the sweet sunset\\
and for the hot night moments,\\
for the fantasy in my bed.\\
\scalebox{0.95}[1]{I take a part of you with me now and you won't get it back}\\
and a part of me will stay here,\\
you can keep it forever, \Em{}dear. Woo\A[7sus4]{}aooooo...\C[add9]{}

\clearpage
\leftskip 40pt
\chorus{}Bye, bye, Hollywood Hills, I'm gonna\\
miss you, wherever I go, I'm gonna\\
come back to walk this streets again,\\
remember that we had fun together. 

Bye, bye, rodeo girls, I'm gonna\\
love you, wherever I go, I'm gonna\\
come back, so we can play together,\\
bye, bye Hollywood Hills forever. 

\verse{3}Long distance love doesn't work,\\
all the miles in between get in your head.\\
No, I don't wanna go, I don't wanna go.

\chorus{}Bye, bye, Hollywood Hills, I'm gonna\\
miss you, wherever I go, I'm gonna\\
come back to walk these streets again,\\
bye, bye\ldots

\chorus{}Bye, bye, Hollywood Hills, I'm gonna\\
miss you, wherever I go, I'm gonna\\
come back to walk these streets again,\\
remember that we had fun together.

Bye, bye, rodeo girls, I'm gonna\\
love you, wherever I go, I'm gonna\\
come back, so we can play together,\\
bye, bye, Hollywood Hills forever.

Hollywood Hills forever,\\
Hollywood Hills forever\\}


\toftagthis{schelinger}
\song{Holubí dům}{Jiří Schelinger}{60pt}{0.93}{
\crdheight=2.3ex
\verse{1}{}\Em{}Zpí - \D{}vám \C[maj7]{}ptákům a \Hm[7]{}zvlášť holu\Em{}bům,\\
stá\D{}val v \C[maj7]{}údolím \Hm[7]{}mém starý \Em{}dům. \emph{\normalsize \textbf{Fine}}\\
\G{}Ptá\D{}ků \G{}houf zalé\D{}tal ke kro\G{}vům,\\
\Em{}měl\ \ \D{}jsem \C[maj7]{}rád holu\Hm[7]{}bích křídel \Em{}šum.

\vskip -2ex
\verse{2}{}Vlídná dívka jim házela hrách,\\
mávání perutí víří prach.\\
Ptáci krouží a neznají strach,\\
měl jsem rád starý dům, jeho práh.

\vskip -2ex
\chorus{}Hledám \Am[7]{}dům holu\D{}bí, kdopak z \G{}vás cestu \Em{}ví?\\
Míval \Am[7]{}stáj roube\D{}nou, bílý \G{}štít.\\
Kde je \Am[7]{}dům holu\D{}bí a ta \G{}dívka kde \Em{}spí?\\
Vždyť to \Am[7]{}ví, že jsem \Hm{}chtěl pro ni \Em{}žít.

\verse{3}{}Sdílný déšť vypráví okapům,\\
bláhový, kdo hledá tenhle dům.\\
Odrůstáš chlapeckým střevícům,\\
měl jsem rád holubích křídel šum.

\vskip -2ex
\verse{4}{}Nabízej úplatou cokoli,\\
nepojíš cukrových homolí.\\
Můžeš mít třeba zrak sokolí,\\
nespatříš ztracené údolí.\\
\textbf{R: + 1. al Fine}\\
}


\toftagthis{anglicke}
\song{Hotel California}{Eagles}{15pt}{1}{
\capo{2}
\verse{1}
\Am{}On a dark desert highway,\E{} cool wind in my hair,\\
\G{}warm smell of colitas\D{} rising up through the air.\\
\F{}Up ahead in the distance,\C{} I saw a shimmering light\\
\Dm{}My head grew heavy and my sight grew dim,\\
\E{}I had to stop for the night.

\verse{2}
There she stood in the doorway,\\
I heard the mission bell,\\
and I was thinking to myself:\\
\uv{This could be heaven or this could be hell.}\\
Then she lit up a candle\\
and she showed me the way.\\
There were voices down the corridor,\\
I thought I heard them say:

\chorus
\F{}Welcome to the Hotel Cali\C{}fornia,\\
such a \E{}lovely place, such a \Am{}lovely face.\\
\F{}Plenty of room at the Hotel Cali\C{}fornia,\\
any \Dm{}time of year you can \E{}find it here.
\clearpage
\verse{3}
Her mind is Tiffany-twisted, she got a Mercedes Benz,\\
she got a lot of pretty, pretty boys that she calls friends.\\
How they dance in the courtyard, sweet summer sweat.\\
Some dance to remember, some dance to forget.

\verse{4}
So I called up the captain: \uv{Please bring me my wine}\\
\uv{We haven't had that spirit here since 1969.}\\
And still those voices are calling from far away,\\
wake you up in the middle of the night,\\
just to hear them say:\\
\textbf{R:}

\verse{5}
Mirrors on the ceiling,\\
the pink champagne on ice, (and she said,)\\
\uv{We are all just prisoners here, of our own device.}\\
And in the master's chambers\\
They gathered for the feast,\\
They stab it with their steely knives,\\
but they just can't kill the beast. 

\verse{6}
Last thing I remember, I was running for the door,\\
I had to find the passage back to the place I was before.\\
\uv{Relax,} said the night man,\\
\uv{we are programed to receive.\\
You can check out any time you like,\\
but you can never leave.}

\chorus{}Welcome to the Hotel California,\\
such a lovely place, such a lovely face.\\
They livin' it up at the Hotel California,\\
what a nice surprise, bring your alibis.
}



\toftagthis{anglicke}
\song{House of the Rising Sun}{The Animals}{45pt}{0.9}{
\verse{1}There \Am{}is \hskip 0.5em a \hskip 0.5em \C{}house in \D{}New Orleans,\F{}\\
they \Am{}call the \C{}Rising \E{}Sun.\\
And it's \Am{}been the \C{}ruin of \D{}many a poor boy\F{}\\
and \Am{}God, I \E{}know, I'm \Am{}one. \hskip 0.5em \E{}

\verse{2}My mother was a tailor,\\
she sewed my new blue jeans,\\
my father was a gamblin' man\\
down in New Orleans.

\verse{3}Now the only thing a gambler needs\\
is a suitcase and trunk\\
and the only time he's satisfied\\
is when he's on a drunk.

\verse{4}Oh, mother, tell your children\\
not to do what I have done.\\
Spend your lives in sin and misery\\
in the House of the Rising Sun

\verse{5} Well, I got one foot on the platform,\\
the other foot on the train.\\
I'm goin' back to New Orleans\\
to wear that ball and chain.

\verse{6}There is a house\dots
}

\toftagthis{ceskekapely}
\song{Hrobař}{Premier}{70pt}{0.92}{
\verse{1}{}V \G{}mládí jsem se učil hrobařem,\\
\Em{}jezdit s hlínou, jezdit s trakařem,\\
\C{}kopat hroby byl můj ide\D{}ál. 

\verse{2}{}Jezdit s hlínou, jezdit s vozíkem,\\
s černou rakví, bílým pomníkem,\\
toho bych se nikdy nenadál.

\verse{3}V mládí jsem se\dots

\verse{4}Jezdit s hlínou\dots

\verse{5}{}Že do módy přijde kremace,\\
černý hrobař bude bez práce,\\
toho bych se nikdy nenadál. 

\verse{6}{}Kolem projel vůz milionáře,\\
záblesk světel pad' mi do tváře,\\
marně skřípěj' kola brzdící. 

\verse{7}{}Stoupám vzhůru, stoupám ke hvězdám,\\
tam se s černou rakví neshledám,\\
sbohem, bílé město zářící. 

\verse{8}{}Sbohem, moje město,\\
vzpomínat budu přesto\\
jak jsem poznal tvůj smích a tvůj pláč!\\
Na na na\ldots{}\\

}

\toftagthis{cechomor}
\song{Hruška}{Čechomor}{90pt}{1}{
\verse{1}\D{}Stojí hruška v širém poli,\\
vršek se jí zelená.\\
\revrpt{} Pod ní se pase kůň vraný,\\
pase ho má milá. \rpt{}

\verse{2}Proč \D{}má milá dnes \A{}pasete,\\
z ve\D{}čera \G{}do rá\A{}na?\\
\revrpt{} Kam, \D{}můj mi\G{}lý, po\A{}jede\D{}te,\\
já \D{}poje\A{}du s v\D{}áma. \rpt{}

\verse{3}Ó, já pojedu daleko,\\
přes vody hluboké.\\
\revrpt{} Kéž bych byl nikdy nepoznal\\
panny černooké. \rpt{}\\
}


\toftagthis{folk}
\song{Husličky}{Vlasta Redl}{30pt}{1}{
\verse{1}{}\revrpt{} \A{}Čí že ste, husličky, \D{}či - \A{}e, \Hm{}kdo vás tu \Fsm{}zanech\E{}al? \rpt{}\\
\Hm{}Na trávě pová\A{}lané\D{}, \hskip 0.8em  \Hm{}na trávě \E{}pová\A{}lané,\D{}\\
\Hm{}u paty \Fsm{}oře - \E{}cha?\Hm{} \hskip 2.2em \Fsm{} \hskip 2.5em \E{}

\verse{2}{}\revrpt{} A \A{}kdože tu trávu tak \D{}zvá\A{}lal, \Hm{}aj modré \Fsm{}fia \hskip 0.4em - \hskip 0.4em \E{}ly, \rpt{}\\
\Hm{}že ste, hu\E{}sli - \E[/G$\sharp$]{}čky, \hskip 1em \A{}sa - \A[/C$\sharp$]{}mé, \hskip 1em \D{}\\
\Hm{}že ste, hu\E{}sli - \E[/G$\sharp$]{}čky, \hskip 1em \A{}sa - \A[/C$\sharp$]{}mé, \hskip 1em \D{}\\
\Hm{}na světě \Fsm{}zosta - \E{}ly?\Hm{} \hskip 2.2em \Fsm{} \hskip 2.5em \E{}

\verse{3}{}\revrpt{} A který tu mládenec usnul a co sa mu přišlo zdát, \rpt{}\\
co sa mu enem zdálo, bože, co sa mu enem zdálo,\\
že už vjec nechtěl hrát?

\verse{4}{}\revrpt{} Zahrajte, husličky, samy, zahrajte zvesela, \rpt{}\\
až sa tá bude trápit, až sa tá bude trápit,\\
která ho nechtěla.\\
}


\toftagthis{filmove}
\song{Hvězda na vrbě}{K. Mareš / J. Šteidl}{25pt}{1}{
\verse{1}\Em{}Kdo \G{}se \Am{}večer\Em{} hájem \Am{}vrací,\F{} ten ať \Em{}klopí\G[7]{} zra\C{}ky, \Em{}\\
ať \G{}je \Am{}nikdy\Em{} neo - \Am{}brací\Dm{} k vr\G[7]{}bě \hskip 0.5em \Em{}křivola\E{}ký.\A{} \hskip 1em \C{} \hskip 1em \Em{}\\
Ji\G{}nak \Am{}jeho \Em{} oči \hskip 0.5em \Am{}zjistí,\F{} i když \Em{}se to\G[7]{} nez\C{}dá,\Em{}\\
že\G{} na \Am{}vrbě \Em{} kromě \Am{}listí, \Dm{} visí \hskip 0.5em \F{}malá hvěz\Am{}da.

\chorus{}Vidě\C{}li jsme jednou v \F{}lukách,
plakat \C{}na tý vrbě \F{}kluka,\\
který \Dm{}pevně věřil \Bb[7]{}tomu,
že ji \D[7]{}sundá z toho \G[7]{}stromu.\Em{}

\verse{2}Kdo o hvězdy jeví zájem, zem když večer chladne,\\
ať jde klidně přesto hájem, hvězda někdy spadne.\\
Ať se pro ni rosou brodí a pak vrbu najde si,\\
a \G{}pro \Am{}ty co\Em{} kolem \Am{}chodí\Dm{} na tu \F{}větev\F{} zavě\Am{}sí.

\optVerse{-35pt}{27pt}{20pt}{
\verse{3}Kdo se večer\ldots\\
\textbf{R:}

\verse{4}Kdo o hvězdy\ldots
}
}
