\toftagthis{nohavica}
\song{Ladovská zima}{Jaromír Nohavica}{30pt}{1}{
\capo{5}
\verse{1}
\C[add9]{}Za vločkou vločka\G[6]{} z oblohy padá,\\
\D[sus2/F$\sharp$]{}chvilinku počká\G[6]{} a potom taje.\\
Na staré sesli sedí pan Lada,\\
obrázky kreslí zimního kraje.

\chorus{}Ladovská zima za okny je\\
a srdce jímá bílá nostalgie,\\
ladovská zima, děti a sáně,\\
a já jdu s nima do chrámu Páně.\\
Bim bam bim bam bim bam\\
bim bam bim bam bim.

\rec{To mokré bílé svinstvo padá mi za límec,\\
už čtvrtý měsíc v jednom kuse furt prosinec.\\
Večer to odhážu, namažu záda,\\
ráno se vzbudim a zas kurva padá.\\
Děcka majú zmrzlé kosti,\\
sáňkujú už jenom z povinnosti.\\
Mrzne jak sviňa, třicet pod nulu,\\
auto ani neškytne, hrudky se dělají v Mogulu.\\
Kolony aut, krok, sun, krok,\\
bo silničáři, tak jak každý rok,\\
jsou překvapeni velice,\\
že sníh zasypal jim silnice.\\
Pendolino stojí kdesik u Polomi,\\
zamrzly mu všecky CD-ROMy.\\
A policajti? Ti to jistí z dálky,\\
zalezlí do Aralky.}\\
\textbf{R:}

\rec{Na Vysočině zavřeli Dé jedničku,\\
kamiony hrály na honičku,\\
tzv. rallye Letní gumy,\\
v tym kopcu u Meziříčí,\\
spěchali s melounama a teď jsou v… (však víte kde).\\
Na ČT1 Studio sníh,\\
Voldanová sedí na saních.\\
A v Praze kalamita jak na Sibiři,\\
tři centimetry sněhu a u Muzea čtyři.\\
Jak v dálce vidím zasněžený Říp,\\
říkám si: Praotče Čechu, tys byl ale strašný cyp.\\
Kdyby jsi popošel ještě o pár kilometrů dále,\\
tak jsem se teďka mohl kdesi v teple v plavkách válet.\\
Místo toho aby se člověk bál zajít do Tesca na nákupy,\\
jak jsou tam na tych rovných střechách sněhu kupy.\\
Do toho všeho jak mám zmrzlý nos aj líca,\\
tak ještě z rádia provokatér Nohavica.\\}
\textbf{R:}
}


\toftagthis{kryl}
\song{Lásko}{Karel Kryl}{45pt}{0.95}{
\verse{1}\Am{}Pár zbytků pro krysy na misce od guláše,\\
\E{}milostný dopisy, s partií\Dm{} mariáše.\\
Před cestou dalekou zpocený boty zujem\\
\C{}a potom pod dekou \E{}sníme, když onanujem.

\vskip -2ex
\chorus{}\Am{}Lásko, \G{}zavři se do pokoje,\\
\Am{}lásko, \G{}válka je holka moje,\\
s \C{}ní se \G{}milu\Am{}ji, když \G{}noci si \Am{}krátím\E{}.\\
Lásko, slunce máš na vějíři,\\
lásko, dvě třešně na talíři,\\
ty ti daruji, až jednou se vrátím.

\verse{2}Dvacet let necelých, odznáček na baretu,\\
s úsměvem dospělých vytáhnem cigaretu,\\
v opasku u boku nabitou parabelu,\\
zpíváme do kroku pár metrů od bordelu.\\
\textbf{R:}

\verse{3} Pár zbytků pro krysy a taška na patrony,\\
latrína s nápisy, jež nejsou pro matróny,\\
není čas na spaní, smrtka nám drtí palce,\\
nežli se zchlastaní svalíme na kavalce.\\
\textbf{R:} Levá, dva!\\
\textbf{R:}\\
}


\toftagthis{filmove}
\song{Lásko má, já stůňu}{Karel Svoboda}{25pt}{1}{
\capo{4}

\verse{1}{}\Am{}Já, ač mám spánek \Em{}bezesný, mně \D{}včera \E{}sen se \Am{}zdál.\\
\Am{}I když dávno \Em{}nejsem s ním, mě \D{}navští\E{}vil sám \F{}král, \G{}řekl:

\chorus{}\uv{\C{}Lásko má, já \G{}stůňu, svoji \Dm{}pýchu já jen \Am{}hrál,\\
kvůli \C[7]{}vám se vzdávám \F{}trůnu, kleno\C{}tů i \G{}kate\E{}drál.}

\verse{2}{}Ač den mám jindy poklidný, dnes nevím, kudy kam.\\
Trápí mě sen ošidný a trápí mě král sám, řekl:

\chorus{}\uv{Lásko má,\ldots{}\\
\hskip 1em \ldots{}klenotů i kate\C{}drál.} \G{}Řekl:

\chorus{}\uv{Lásko má,\ldots{}\\
\hskip 1em \ldots\ klenotů i kate\A{}drál.}\\
}


\toftagthis{anglicke}
\song{Leaving on a Jet Plane}{John Denver}{50pt}{1}{
\verse{1}All my \C{}bags are packed, I'm \F{}ready to go,\\
I'm \C{}standing here out\F{}side your door,\\
I \C{}hate to wake you \F{}up to say good\G{}bye. 

\verse{2}But the dawn is breaking, it's early morn,\\
the taxi's waiting, he's blowing his horn,\\
already, I'm so lonesome I could die. 

\chorus{}So kiss me and smile for me,\\
tell me that you'll wait for me,\\
hold me like you'll never let me go. 

'Cause I'm leaving on a jet plane,\\
don't know when I'll be back again,\\
oh, babe, I hate to go. 

\verse{3}{}There's so many times I've let you down,\\
so many times I've played around,\\
I tell you now they don't mean a thing. 

\verse{4}Every place I'll go I think of you,\\
every song I sing I'll sing for you,\\
when I come back,  I'll bring your wedding ring.\\
\textbf{R:} 
\clearpage
\verse{5}{}Now the time has come to leave you,\\
one more time let me kiss you,\\
then close your eyes, I'll be on my way. 

\verse{6} Dream about the days to come,\\
when I won't have to leave alone,\\
about the times, I won't have to say.\\
\textbf{R: + $\downarrow$}

I'm leaving on a jet plane,\\
don't know when I'll be back again,\\
oh, babe, I hate to go.\\
}


\toftagthis{anglicke}
\song{Lemon Tree}{Fool's Garden}{30pt}{1}{
\verse{1}{}I'm \Dm{}sittin' here in the \Am{}boring room,\\
it's just another rainy Sunday afternoon,\\
I'm wasting my time, I got nothing to do,\\
I'm hangin' around, I'm waitin' for you\\
but \Gm{}nothing ever happens\Am{} -- and I \Dm{}wonder.

\verse{2}{}I'm drivin' around in my car,\\
I'm drivin' too fast, I'm drivin' too far,\\
I'd like to change my point of view,\\
I feel so lonely, I'm waiting for you\\
but nothing ever happens -- and I wonder.

\chorus{}I \F{}wonder how, \C{}wonder why\\
\Dm{}yesterday you told me 'bout the \Am{}blue blue sky\\
and \Bb{}all that I can \C{}see\\
is just a yellow \F{}lemon tree\C{}.\\
I'm \F{}turnin' my head \C{}up and down,\\
i'm \Dm{}turnin' turnin' turnin' turnin' \Am{}turnin' around\\
and \Bb{}all that I can \H[dim]{}see\\
is just a yellow \C{}lemon tree\C[7]{}.

Ta, da da didap\ldots{}

\verse{3}{}I'm sittin' here, I miss the power,\\
I'd like to go out, takin' a shower\\
but there's a heavy cloud inside my head,\\
I feel so tired, put myself into bed\\
Where nothing ever happens -- and I wonder.

\verse{*}{}\A{}Isolation \Dm{}is not good for me,\\
\C{}isolation -- \F{}I don't want to \A{}sit on a lemon tree.

\verse{4}{}I'm steppin' around in a desert of joy,\\
baby, anyhow I get another toy\\
and everything will happen -- and you'll wonder.\\
\textbf{R: + $\downarrow$}

I \F{}wonder how, \C{}wonder why\\
\Dm{}yesterday you told me 'bout the \Am{}blue blue sky\\
and \Bb{}all that I can \C{}see\\
and \Bb{}all that I can \C{}see\\
and \Bb{}all that I can \C{}see\\
is just a yellow \F{}lemon tree.\\
}

\toftagthis{anglicke}
\song{Let It Be}{The Beatles}{55pt}{0.9}{
\verse{1}{}When I \C{}find myself in \G{}times of trouble,\\
\Am{}Mother Mary \F{}comes to me\\
\C{}speaking words of \G{}wisdom -- let it \F{}be.\C{} \hskip 0.8em \Dm{} \hskip 2em \C{}\\
And in my hour of darkness\\
she is standing right in front of me,\\
speaking words of wisdom -- let it be.

\chorus{}Let it \Am{}be, let it \G{}be, let it \F{}be, let it \C{}be,\\
\C{}whisper words of \G{}wisdom -- let it \F{}be. \C{} \hskip 0.8em \Dm{} \hskip 2em \C{}

\verse{2}{}And when the broken-hearted people\\
living in the world agree,\\
there will be an answer -- let it be.\\
For though they may be parted\\
there is still a chance that they will see,\\
there will be an answer -- let it be.

\chorus{}Let it be, let it be, let it be, let it be,\\
there will be an answer -- let it be.\\
Let it be, let it be, let it be, let it be,\\
whisper words of wisdom -- let it be.\\
Let it be, let it be, let it be, let it be,\\
there will be an answer -- let it be.\\
~\\
\F{} \hskip 1em \C{} \hskip 0.8em \Dm{} \hskip 2em \C{} \hskip 2em \Bb{} \hskip 1em \F[/A]{} \hskip 1.8em \G{} \hskip 1.5em \F{} \hskip 1.5em \C{}\\

\verse{3}{}And when the night is cloudy\\
there is still a light that shines on me,\\
shine on 'till tomorrow -- let it be.\\
I wake up to the sound of music,\\
Mother Mary comes to me\\
there will be no sorrow -- let it be.

\chorus{}Let it be, let it be, let it be, let it be,\\
there will be no sorrow -- let it be.\\
Let it be, let it be, let it be, let it be,\\
whisper words of wisdom -- let it be.
~\\
\F{} \hskip 1em \C{} \hskip 0.8em \Dm{} \hskip 2em \C{} \hskip 2em \Bb{} \hskip 1em \F[/A]{} \hskip 1.8em \G{} \hskip 1.5em \F{} \hskip 1.5em \C{}\\

}

\toftagthis{anglicke}
\song{Lion Sleeps Tonight}{The Tokens}{60pt}{1}{
\capo{1}
~\\
\verse{1}\E{}In the jungle, the \A{}mighty jungle,\\
the \E{}lion sleeps to\H{}night.\\
In the jungle, the quiet jungle,\\
the lion sleeps tonight.

\verse{2}Near the village, the peaceful village,\\
the lion sleeps tonight.\\
near the village, the quiet village,\\
the lion sleeps tonight.

\verse{3}Hush my darling, don't fear my darling,\\
the lion sleeps tonight.\\
Hush my darling, don't fear my darling,\\
the lion sleeps tonight.\\
}


% NEW SONGS
\toftagthis{sverakuhlir}
\song{Lotr intelektuál}{Z. Svěrák / J. Uhlíř}{40pt}{1}{
\medskip
\rec{Vykoupat! Odvšivit! Učesat! Voblíct!\\
Ráno půjde do školy!\\
Tu nejlepší školu mu dám! (Správně!)\\
Protože na to mám! (Správně!)}

\verse{1}\Am{}Dáme klukovi ško\Em{}ly,\hskip 1.2em \F{}ať to stojí coko\C{}li,\\
\G{}nešetříme na chlap\C{}ci, \F{}táto, \C{}šáhni \G{}do kap\C{}sy.

Když zná lupič písmena, stane se s ním proměna,\\
když zná lupič dějiny, tak je úplně jiný.

\chorus{}\C{}Bude \F{}to ozdoba \C{}loupežnické \G{}bandy,\\
\C{}bude \F{}mít brejličky \C{}a možná i \G{}kšandy,\\
\C{}posu\F{}ne řemeslo \C{}zas o kousek \G{}dál,\\
\C{}bude to \F{}lotr \G{}intelektu\C{}ál.

\verse{2}Naučí se francouzsky, bude nosit licousky,\\
naučí se mluvnici, \uv{přelstí všecky pravnici.}

Naučí se německy, řekne troky, ne necky,\\
když bude mluvit plynně, může loupit v cizině.\\
\textbf{R:}\\	
}
