\toftagthis{anglicke}
\song{Tears in Heaven}{Eric Clapton}{70pt}{0.85}{
\verse{1}\A{}Would you \E[/G$\sharp$]{} know my \Fsm{}name\\
\D[/F$\sharp$] if \hskip 0.2em I \hskip 0.2em s\A[/E]aw you in \E{}heaven?\\
Would it be the same\\
if I saw you in heaven?

\chorus{}\Fsm{}I must be \Cs[/F]{}strong,\A[7/E]{} and carry \Fs{}on,\\
'cause I \Hm[7]{}know I don't be\E[7sus4]{}long\\
here in hea\A{}ven.

\verse{2}Would you hold my hand\\
if I saw you in heaven?\\
Would you help me stand\\
if I saw you in heaven?

\chorus{}I'll find my way, through night and day,\\
'cause I know I just can't stay\\
here in heaven.

\verse{*}\C{}Time can \G[/H]{}bring you \Am{}down,\\
time can \D[/F$\sharp$]{}bend your \G{}knee.\D[/F$\sharp$]{} \hskip 2.5em \Em{} \hskip 2em \D[/F$\sharp$]{} \hskip 2.5em \G{}\\
Time can break your heart,\\
have you begging, please,\\
begging, please.\\
\vskip 7pt
(instrumental)\\
\vskip 10pt

\clearpage
\chorus{}Beyond the door,\\
there's peace I'm sure.\\
And I know there'll be no more\\
tears in heaven.

\verse{3. = 1}\\
\textbf{R: + }Cause I know I don't belong\\
here in heaven.\\}




\toftagthis{folk}
\songWithTranslation{czech}{
\song{Ten vítr to ví}{Waldemar Matuška}{70pt}{0.85}{
\crdheight=2.0ex
\verse{1}\D{}Míle a \G{}míle jsou \D{}cest, které znám,\\
jdou trávou i \G{}úbočím \A{}skal,\\
\D{}jsou cesty \G{}zpátky a \D{}jsou cesty \Hm{}tam\\
a \D{}já na všech \G{}s vámi \A{}stál.\A[7]{}\\
\D{}Proč ale \G{}blátem nás \D{}kázaly vést\\
a špínou nám \G{}třísnily \D{}šat?

\vskip -1.5ex
\chorus{}To \G{}ví snad jen \A{}déšť a \D{}vítr kolem \Hm{}nás,\\
ten \G{}vítr, co \A[7]{} začal právě \D{}vát.

\verse{2}Míle a míle se táhnou těch cest\\
a dál po nich zástupy jdou.\\
Kříže jsou bílé a lampičky hvězd\\
jen váhavě svítí tmou.\\
Bůh ví, co růží, jež dál mohly kvést,\\
spí v hlíně těch práchnivých blat?\\
\textbf{R:}

\verse{3}Dejte mi stéblo a já budu rád,\\
i stéblo je záchranný pás.\\
Dejte mi flétnu a já budu hrát\\
a zpívat a ptát se vás:\\
Proč jen se účel tak rád mění v bič\\
a proč že se má člověk bát ?\\
\textbf{R:}\\
}
}{english}{
\originalVersion{Blowin' in the Wind}{Bob Dylan}{60pt}{1}{
\verse{1}\noprint{\D{}}How many \noprint{\G{}}roads must a \noprint{\D{}}man walk down\\
before they \noprint{\G{}}call him a \noprint{\A{}}man?\\
\noprint{\D{}}How many \noprint{\G{}}seas must a \noprint{\D{}}white dove \noprint{\Hm{}}sail\\
be\noprint{\D{}}fore she \noprint{\G{}}sleeps in the \noprint{\A{}}sand?\noprint{\A[7]{}}\\
\noprint{\D{}}How many \noprint{\G{}}times must the \noprint{\D{}}cannon balls fly\\
before they're \noprint{\G{}}forever \noprint{\D{}}banned?

\chorus{}The \noprint{\G{}}answer, my \noprint{\A{}}friend, is \noprint{\D{}}blowin' in the \noprint{\Hm{}}wind,\\
the \noprint{\G{}}answer is \noprint{\A[7]{}}blowin' in the \noprint{\D{}}wind.

\verse{2}How many years can a mountain exist\\
before it is washed to the sea?\\
How many years can some people exist\\
before they're allowed to be free?\\
How many times can a man turn his head\\
and pretend that he just doesn't see?\\
\textbf{R:}

\verse{3}How many times must a man look up\\
before he can see the sky?\\
How many ears must one man have\\
before he can hear people cry?\\
How many deaths will it take 'til he knows,\\
that too many people have died?

\chorus{}The answer, my friend, is blowin' in the wind.\\
The answer is blowin' in the wind.\\
The answer is blowin' in the wind.\\ 
}
}



\toftagthis{folk}
\song{To tá Heľpa}{lidová}{30pt}{1}{
\verse{1}\Am{}To ta \Dm{}Heľpa, \Am{}to ta \Dm{}Heľpa, \Am{}to je \E{}pekné \Am{}mesto.\\
A v tej Heľpe, a v tej Heľpe švárnych chlapcov je sto.\\
\revrpt{} \F{}Koho je sto, \C{}toho je sto, \G{}nie po mojej \C{}vôli\E{},\\
\Am{}ľen za \Dm{}jedným, \Am{}ľen za \Dm{}jedným, \Am{}srdiečko \E{}ma \Am{}bolí. \rpt{}

\verse{2}Za Janíčkom, za Palíčkom, krok by nespravila,\\
za Ďuríčkom, za Mišíčkom, Dunaj preskočila.\\
\revrpt{} Dunaj, Dunaj, Dunaj, Dunaj, aj to širé more,\\
ľen za jedným, ľen za jedným, počešenie moje. \rpt{}\\
}


\toftagthis{anglicke}
\song{Total Eclipse of the Heart}{Bonnie Tyler}{12pt}{1}{
\verse{1}\Am{}Turn around, every now and then I get a \G{}little bit\\
lonely and you're never coming round.\\
Turn around, every now and then I get a little bit\\
tired of listening to the sound of my tears.

\vskip -2ex
\C{}Turn around, every now and then I get a \Bb{}little bit\\
nervous that the best of all the years have gone by.\\
Turn around, every now and then I get a little bit\\ 
terrified and then I see the look in your eyes.

\vskip -2ex
\scalebox{.97}[1.0]{\Eb{}Turn around, \Ab[maj7]{}bright eyes, every now and then I fall apart.}\\
\scalebox{.97}[1.0]{\Eb{}Turn around, \Ab[maj7]{}bright eyes, every now and then I fall a\Am{}part.}

\verse{2}Turn around, every now and then I get a little bit\\
restless and I dream of something wild.\\
Turn around, every now and then I get a little bit\\ 
helpless and I'm lying like a child in your arms.

Turn around, every now and then I get a little bit\\ 
angry and I know I've got to get out and cry.\\
Turn around, every now and then I get a little bit\\ 
terrified but then I see the look in your eyes.

Turn around bright eyes, every now and then I fall apart.\\
Turn around bright eyes, every now and then I fall a\G{}part.

\scalebox{.95}[1.0]{\chorus{}And I \Em{}need you now \C{}tonight, and I \D{}need you more than \G{}ever}\\
\scalebox{.95}[1.0]{And if you'll only hold me tight, we'll be holding on forever.}\\
\scalebox{.95}[1.0]{And we'll only be making it right, cause we'll \D{}never be wrong} 

To\Em{}gether we can take it to the \D{}end of the line,\\
your \Em{}love is like a shadow on me \A{}all of the time.\\
I \G{}don't know what to do and I'm \D{}always in the dark,\\
we're \Em{}living in a powder keg and \A{}giving off sparks.

I really need you to\G{}night, for\D{}ever's gonna \Hm{}start to\C{}night,\\
for\D{}ever's gonna start tonight.

\verse{*}\G{}Once upon a time I was \Em[7]{}falling in love,\\
but \Hm{}now I'm only falling a\C{}part,\\
there's \Am{}nothing I can do, a \D{}total eclipse of the \G{}heart.

Once upon a time there was light in my life,\\
but now there's only love in the dark,\\
nothing I can say, a total eclipse of the heart 
}


\toftagthis{filmove}
\song{Trezor}{Karel Gott}{5pt}{1}{
\D{}Ze zdi na mě \D[7]{}tupě zírá \G{}po trezoru temná díra,\\
\E[7]{}poznám tedy bez nesnází, \A[7]{}že tam nepochybně něco schází,\\
\D{}ve zdi byl totiž \D[7]{}po dědovi \G{}velký trezor ocelový.\\
\A[7]{}Mám tedy ztrátu zdánlivě minimál\G[7]{}ní. \hskip 0.8em \D{}

Na to, že \A[7]{}náhodně v krámě vášnivé dámě\\
\D{}padl jsem za tro\Hm{}fej,\\
\E[7]{}tvrdila pevně: přijdu tě levně, \A[7]{}nezoufej, ó jé, jé, jé, jé.

\D{}Jenže potom \D[7]{}v naší vile \G{}chovala se zhůvěřile,\\
\textls[-45]{\E[7]{}aby měla správné klima, \A[7]{}dal jsem ji do trezoru, ať v klidu dřímá.}\\
\textls[-30]{\D{}Spánku se bráním \D[7]{}už noc pátou, \G{}ne ale žalem nad tou ztrátou,}\\
\A[7]{}jen hynu bázní, že kasař úlovek \G[7]{}vrá - \D{}tí.

Na to, že\ldots{}
}


%\toftagthis{matuska}
%\song{Třešně zrály}{Waldemar Matuška}{30pt}{0.85}{
%\verse{1}\C{}Jó, třešně zrály, \G[7]{}zrovna třešně \C{}zrály,\\
% \C{}sladký \E[7]{}třešně \Am{}zrály a \F{}teplej \G[7]{}vítr \C{}vál.\\
%A já k horám v dáli, k modrejm horám v dáli,\\
% sluncem, který pálí, tou dobou stádo hnal.\\
%\chorus{}\C{}Jó, \G[7]{}třešně \Am{}zrály, \Dm[7]{}zrovna \G[7]{}třešně \C{}zrály,\\
% \C{}sladký \E[7]{}třešně \Am{}zrá - \F{}ly a \Dm{}jak to \G[7]{}bylo \C{}dál? 
%
%\verse{2}Tam, jak je ta skála, ta velká bílá skála,\\
% tak tam vám holka stála a bourák opodál.\\
%A moc se na mě smála, zdálky už se smála,\\
% i zblízka se pak smála a já se taky smál.\\
%\textbf{R:}\\
%\verse{3}Řekla, že mě má ráda, už dlouho mě má ráda,\\
% dlouho mě má ráda, abych prej si ji vzal.\\
%Ať nechám ty svý stáda, že léta pilně střádá,\\
% jen abych ji měl rád a žil s ní jako král.\\
%\textbf{R:}\\
%\verse{4}Pokud je mi známo, já řek' jenom: \uv{Dámo,\\
% milá hezká dámo, zač bych potom stál.\\
% Ty můj typ nejsi, já mám svoji Gracie,\\
% moji malou Gracie, a tý jsem srdce dal.}\\
%\textbf{R:}\\
%\verse{5}Jó, u tý skály dál třešně zrály,\\
% modrý hory v dáli, teplej vítr vál.\\
%A já od tý skály, od tý bílý skály,\\
%v slunci, který pálí, jsem hnal svý stádo \C{}dá - \Ab{}á - \C{}ál.\\
%
%}

\toftagthis{folk}
\song{Tři kříže}{Hop Trop}{60pt}{0.95}{
\verse{1}\Dm{}Dávám sbohem \C{}břehům prokla\Am{}tejm,\\
který \Dm{}v drápech má \C{}ďábel \Dm{}sám.\\
\Dm{}Bílou přídí \C{}šalupa \uv{My \Am{}Grave}\\
míří \Dm{}k útesům, \C{}který \Dm{}znám.

\chorus{}Jen tři \F{}kříže z bí\C{}lýho kame\Am{}ní\\
někdo \Dm{}do písku \C{}posklá\Dm{}dal.\\
Slzy \F{}v očích měl a \C{}v ruce znave\Am{}ný\\
lodní \Dm{}deník, co \C{}sám do něj \Dm{}psal.

\verse{2}První kříž má pod sebou jen hřích,\\
samý pití a rvačky jen.\\
Chřestot nožů, při kterým přejde smích,\\
srdce kámen a jméno \uv{Stan}.\\
\textbf{R:}

\verse{3}Já, Bob Green, mám tváře zjizvený,\\
štěkot psa zněl, když jsem se smál.\\
Druhej kříž mám a spím pod zemí,\\
že jsem falešný karty hrál.\\
\textbf{R:}

\verse{4}Třetí kříž snad vyvolá jen vztek,\\
Fatty Rogers těm dvoum život vzal.\\
Svědomí měl, vedle nich si klek'\ldots{}

\rec{Snad se chtěl modlit: \uv{Vím, trestat je lidský,\\
ale odpouštět božský. Snad mi tedy Bůh odpustí.}}

\chorus{}Jen tři kříže z bílýho kamení\\
jsem jim do písku poskládal.\\
Slzy v očích měl a v ruce znavený\\
lodní deník, a v něm, co jsem psal.\\
}
