\toftagthis{anglicke}
\song{Wake Me Up When September Ends}{Green Day}{50pt}{1}{
\crdheight=2.5ex
\verse{1}\D{}Summer has \D[/C$\sharp$]{}come and passed,\\
\D[/H]{}the innocent can \D[/A]{}never last.\\
\G{}Wake me up \Gm{}when September \D{}ends.

\verse{2}Like my father's come to pass,\\
seven years has gone so fast.\\
\G{}Wake me up \Gm{}when September \D{}ends.\D[/C$\sharp$]{}

\chorus{}\Hm{}Here comes the \Fsm{}rain again,\\
\G{}falling from the \D{}stars,\D[/C$\sharp$]{}\\
\Hm{}drenched in my \Fsm{}pain again,\\
\G{}becoming who we \A{}are.

\verse{3}As my memory rests,\\
but never forgets what I lost.\\
Wake me up when September ends

\verse{4}Summer has come and passed\ldots 
\clearpage
\verse{5}Ring out the bells again\\
like we did when spring began.\\
Wake me up when September ends.\\
\textbf{R:}

\verse{6}As my memory rests\ldots 

\verse{7}Summer has come and passed\ldots 

\verse{8}Like my father's come to pass,\\
twenty years has gone so fast.\\
\revrpt{} Wake me up when September ends. \rpt{} $^{3\times}$

}


\toftagthis{anglicke}
\song{What a Wonderful World}{Louis Armstrong}{20pt}{1}{
\verse{1}I see \C{}trees of \Em{}green,\F{} red roses \Em{}too,\\
\Dm[7]{}I see them \C{}bloom,\E[7]{} for me and \Am{}you,\\
and I \Ab{}think to myself:\Dm[7]{} \uv{What a \G[7]{}wonderful wo\C{}rld.}\C[+]{} \hskip 1.5em \F[maj7]{} \hskip 3em \G[7]{}\\
\verse{2} I see skies of blue and clouds of white,\\
the bright blessed day, the dark sacred night\\
and I think to myself: \uv{What a wonderful wo\C{}rld}\F{} \hskip 0.8em \F{} \hskip 0.8em \C{}

\verse{*}The \G[7]{}colors of the rainbow, so \C{}pretty in the sky,\\
are \G[7]{}also on the faces of \C{}people goin' by.\\
I see \Am{}friends shaking \G[/H]{}hands, saying:\Am[/C]{} \uv{How do you \G{}do?}\\
\Am[/C]{}They're really \Cs[dim]{}saying: \uv{\Dm[7]{}I \hskip 2em \Cs[dim]{}love\hskip 1.7em \G[7]{}you.} 

\verse{3}I hear babies cry, I watch them grow,\\
they'll learn much more than I'll ever know,\\
and I think to myself: \uv{What a wonderful wo\C{}rld\Em[7b5]{}.}\\
\A[7]{}Yes, I \Dm[7]{}think to myself:\Dm[7/G]{} \uv{What a \G[7]{}wonderful \C{}world.}\F[6]{} \hskip 1.2em \C{}\\
}


\toftagthis{anglicke}
\song{While My Guitar Gently Weeps}{The Beatles}{35pt}{1.05}{
\medskip 

\verse{1}I \Am{}look at you \Am[/G]{}all, see the \D[9/F$\sharp$]{}love there that's \F{}sleeping,\\
\Am{}while my gui\G{}tar gently \D{}weeps.\E[7]{}\\
I \Am{}look at the \Am[/G]{}floor and I \D[9/F$\sharp$]{}see it needs \F{}sweeping,\\
\Am{}still my gui\G{}tar gently \C{}weeps.\E[7]{}

\chorus{}\A{}I don't know \Csm{}why \hskip 0.8em \Fsm{} nobody \Csm{}told you\\
\Hm{}how to unfold your \E{}love.\\
I don't know how someone controlled you,\\
they bought and sold you.

\verse{2}I look at the world and I notice it's turning,\\
while my guitar gently weeps.\\
With every mistake we must surely be learning,\\
still my guitar gently weeps.

\chorus{}I don't know how you were diverted,\\
you were perverted too.\\
I don't know how you were inverted,\\
no one alerted you.

\clearpage
\verse{3}I look from the wings at the play you are staging,\\
while my guitar gently weeps.\\
As I'm sitting here, doing nothing but ageing,\\
still, my guitar gently weeps.

\verse{4} I look at you all, see the love there that's sleeping,\\
while my guitar gently weeps.\\
Look at you all\ldots{}\\
still my guitar gently weeps.\\
}


\toftagthis{anglicke}
\song{Wonderwall}{Oasis}{20pt}{1}{
\vskip 10pt
\crdheight=2.5ex
\verse{1}\Em[7]{}Today is \G{}gonna be the day\\
that they're \D[sus4]{}gonna throw it back to \A[sus4]{}you.\\
By now, you should've somehow\\
realized what you gotta do.\\
I don't believe that anybody\\
feels the way I do about you \C[add9]now. \hskip 1.2em \D[sus4]{} \hskip 3em \A[7sus4]{}

\verse{2} Backbeat, the word is on the street\\ 
that the fire in your heart is out.\\
I'm sure you've heard it all before,\\
but you never really had a doubt.\\
I don't believe that anybody\\
feels the way I do about you now.

\verse{*}And \C[add9]{}all the roads we \D{}have to walk are \Em{}winding\\
and \C[add9]{}all the lights that \D{}lead us there are \Em{}blinding.\\
\C[add9]{}There are many \D{}things that I would \G{}like to \G[/F$\sharp$]{}say to \Em{}you,\\
but I don't know \A[7sus4]{}how.

\clearpage
\chorus{}Because \C[add9]{}maybe \hskip 0.7em \Em[7]{} \hskip 2.3em \G{}you're \Em[7]{}gonna be the one that\\
\C[add9]{}saves me\Em[7]{} \hskip 2.3em \G{}and \Em[7]{}after \hskip 0.5em \C[add9]{}all,\hskip 2em  \Em[7]{} \hskip 2.3em \G{}\\
you're my \Em[7]{}wonder\C[add9]{}wall. \hskip 1em \Em[7]{} \hskip 2.4em \G{} \hskip 1em \Em[7]{}

\verse{3}Today was gonna be the day,\\
but they'll never throw it back to you.\\
By now, you should've somehow\\
realized what you're not to do.\\
I don't believe that anybody\\
feels the way I do about you now.

\verse{*}And all the roads that lead you there were winding\\
and all the lights that light the way are blinding.\\
There are many things that I would like to say to you,\\
but I don't know how.

\textbf{R: $(2\times)$}~\\
I said maybe you're gonna be the one that saves me.\\
You're gonna be the one that saves me.\\
You're gonna be the one that saves me.\\
}
